Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-10-13 SubGenome Analysis.Rmd
Added scatterplots

# Wrapup
***
Report generated on: `r as.character(format(Sys.Date(), format="%B %d, %Y"))`

>>>>

Here is a scatter plot of isoform counts across gene pairs.

```{r subgenome_isoforms_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.align='center'}
# Isoforms
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(geneTranscript.counts, by=c("Maize1"="gene")) %>%
  inner_join(geneTranscript.counts, by=c("Maize2"="gene"))
names(data)[3] <- "Value_maize1"
names(data)[4] <- "Value_maize2"
# data <- subset(data, data$Value_maize1 > 1 & data$Value_maize2 > 1) ## Ignore single-exon genes
data$foldChange <- log2(data$Value_maize1) - log2(data$Value_maize2)

n <-
  data %>%
  subset(Value_maize1 > 100 | Value_maize2 > 100) %>%
  nrow()

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = abs(foldChange))) +
  scale_color_gradient(low = "blue", high = "red") +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  xlim(0,100) +
  ylim(0,100) +
  labs(
    title = paste0("Scatterplot of isoform counts for gene pair(s).\nExcludes ",n," outlier, alpha=.1, foldchange in log2."),
    x = "Isoform Counts for Maize1 Gene",
    y = "Isoform Counts for Maize2 Gene"
  )
plot(plot)
```

```{r subgenome_expression_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.expression.sample.avg, by=c("Maize1"="geneID")) %>%
  inner_join(maize.expression.sample.avg, by=c("Maize2"="geneID", "Sample"="Sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, Sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = Sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of expression for gene pair(s).\nAlpha=.1"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Expression for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~Sample, nrow=6)
plot(plot)
```

```{r subgenome_protein_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.protein.abundance.sample.avg, by=c("Maize1"="geneID")) %>%
  inner_join(maize.protein.abundance.sample.avg, by=c("Maize2"="geneID", "Sample"="Sample")) %>%
  subset(!is.na(dNSAF_avg.x) & !is.na(dNSAF_avg.y))
names(data)[4] <- "Value_maize1"
names(data)[5] <- "Value_maize2"
# data <- subset(data, Sample %in% c("Silk", "Embryo 20 DAP", "Leaf Zone 2 (Stomatal)"))

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = Sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~Sample, nrow=6)
plot(plot)
```
# Wrapup
***
Report generated on: `r as.character(format(Sys.Date(), format="%B %d, %Y"))`
